Visualization of [fulle name] Fractional Integrals

### 2019-03-25 fractional/CMJ style files/article-template.tex
started introduction

\title{Visualization of Fractional Integrals}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

\noindent
The \textit{College Mathematics Journal} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
\begin{itemize}
\item times
\item pifont
\item graphicx
\item color
\item AMS styles: amsmath, amsthm, amsfonts, amssymb
\item url
\end{itemize}
Use of other \LaTeX\ packages should be minimized as much as possible. Math notation, like $c = \sqrt{a^2 +b^2}$, can be left in \TeX's default Computer Modern typefaces for manuscript preparation; or, if you have the appropriate fonts installed, the \texttt{mathtime} or \texttt{mtpro} packages may be used, which will better approximate the finished article.

Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.

>>>>

\title{Visualization of [fulle name] Fractional Integrals}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

It can be argued that fractional calculus is as old as classical calculus itself. The father of calculus, Leibnis, mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers a question L'Hospital poses. Liouville and Riemann laid much of the groundwork which was 
needed to define the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is quite useful from 
a pedigogical point of view as
